### 2014-03-15 Draft/example.tex
Revised Example Section

We now present some real world examples to motivate our approach. In particular, through these examples, we demonstrate that developers often ignore the tempral specifications of an API present in its documentation. We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
pages. For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages. Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation. 
If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.45]{Stackoverflow.eps}
\end{center}
\caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
\end{figure}

Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is a question and answer site for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon.
The document clearly states that before deleting the bucket, the objects in the buckets must be deleted. \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.

%\begin{figure}[t]
%\begin{center}
%\includegraphics[scale=0.5]{AmzonS3DeleteBucketAPI.eps}
%\end{center}
%\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
%\end{figure}

Formal verification tools can be used to easily find such kind of defects.
However, formal analysis tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal or machine understandable format. 
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation. In next section, we briefly discuss the related work in this area.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{Example2.eps}
\end{center}
\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
\end{figure}

>>>>

We next present a real world example to motivate our approach.
In particular, through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
For instance, the PDF version of the documentation for \amazonAPI\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
Developers often may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
resulting in defective client applications that invoke API methods in sequences prohibited by documentation.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.45]{Stackoverflow.eps}
\end{center}
\caption{\label{fig:Stackoverflow} The Query posted on Stack Overflow forum regrading Amazon S3 REST API}
\end{figure}

Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the constraints in \amazon.
The API document pertaining to the  delete bucket functionality clearly states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but one of the responses on the forum encouraged the person asking query to switch to another product,
thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.

The preceding issue can be easily detected using formal analysis tools.
For instance, a specification rule (a temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our proposed approach.
